---
title: "Plotting Minute-Level Activity Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plotting Minute-Level Activity Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(actiplot)
```

This vignette uses the packaged `acti_minute_data` accelerometer recording.
It contains seven days of minute-level vector-magnitude activity counts.
It is processed from the [upper-limb activity Figshare
collection](https://springernature.figshare.com/collections/Upper_limb_activity_of_twenty_myoelectric_prosthesis_users_and_twenty_healthy_anatomically_intact_adults_/4457855)
described by [Chadwell et al. (2019)](https://doi.org/10.1038/s41597-019-0211-6).

```{r data}
activity <- acti_minute_data
```

## Complete recording

Use `acti_plot_time()` to inspect activity across the entire recording. The
`breaks` argument accepts ordinary duration strings and sets the interval of
the time-axis labels.

```{r full-time}
acti_plot_time(activity, counts, breaks = "4 hours")
```

For a more legible complete-recording axis, set `x_axis = "12 hours"`. It
shows date and 12-hour-clock labels at midnight and noon. Alternatively,
`x_axis = "midnight"` prints just the date at midnight, without `00:00:00`.

```{r full-time-readable-axis}
acti_plot_time(activity, counts, x_axis = "12 hours")
acti_plot_time(activity, counts, x_axis = "midnight")
```

## Daily aligned rows

Use `acti_plot_day()` to align each day on the same time-of-day axis. Each
facet row is one calendar date, which makes day-to-day activity patterns easy
to compare.

```{r daily}
acti_plot_day(activity, counts, breaks = "4 hours")
```

Set `facet = "month-day"` to remove the year from date strips, or
`facet = "day"` to use the baseline-relative day calculated by
`actibase::acti_separate_times()`.

```{r daily-facet-labels}
acti_plot_day(activity, counts, facet = "month-day")
acti_plot_day(activity, counts, facet = "day")
```

## Date-by-time heat map

`acti_plot_heatmap()` uses the same alignment with counts represented by fill.

```{r heatmap}
acti_plot_heatmap(activity, counts, breaks = "4 hours")
```
